### 2019-04-10 5_evaluation.tex
Remove resolved FIXMEs.
Update evaluation numbers to match chart.

The ratio in METG between 0 and 3 dependencies per task ranges from
$1.3\times$ to $59\times$ (median $3.0\times$). From 1 to 3
dependencies, the ratio varies from $1.2\times$ to $15\times$ (median
$2.1\times$). The difference is most pronounced in systems that
perform runtime work inline. For example, MPI achieves an METG of 390
ns with 0 dependencies, but this rises to 4.6 \textmu{}s with 3 dependencies,
a factor of $12\times$ increase. This is unsurprising as in the case
of 0 dependencies, no \lstinline[language=C++]{MPI_Isend} calls are
issued at all, so MPI has nothing to do aside from executing kernels
as quickly as possible. For this reason, we recommend evaluating the performance of
programming systems under realistic workloads, rather than with
trivial dependencies.

@@

% FIXME: update this when we have more data

@@

% FIXME: remove parsec dtd shard if no space.

% FIXME: talk about overhead spanning 5 orders of magnitude

>>>>

The ratio in METG between 0 and 3 dependencies per task ranges from
$1.01\times$ to $16\times$ (median $2.9\times$). From 1 to 3
dependencies, the ratio varies from $0.54\times$ to $7.3\times$ (median
$1.8\times$). The difference is most pronounced in systems that
perform runtime work inline. For example, MPI achieves an METG of 390
ns with 0 dependencies, but this rises to 4.6 \textmu{}s with 3 dependencies,
a factor of $12\times$ increase. This is unsurprising as in the case
of 0 dependencies, no \lstinline[language=C++]{MPI_Isend} calls are
issued at all, so MPI has nothing to do aside from executing kernels
as quickly as possible. For this reason, we recommend evaluating the performance of
programming systems under realistic workloads, rather than with
trivial dependencies.

@@

@@
